---
title: "Software"
author: "Marcelo Rosales"
date: "2023/05/26"
format: 
  html: 
    code-fold: false
    code-copy: true
    code-overflow: wrap
---

## Flat-field correction (ImageJ macro)

[Download here](https://github.com/dbsb-juntendo/descSPIM/blob/main/FlatfieldCorrection_IJmacro_ver230406.ijm)

> Not available anymore (404 error)

## How to use:

1.  prepare a reference xy image(1) and a sample xyz stack(2).
    (a) a reference xy image In order to get the reference image, hogehoge... acquired using dye-solving solution (e.g., CUBIC-R + FITC reagent)...
    (b) a sample xyz image stack to be corrected
2.  run macro with ImageJ/Fiji

### Tiling light-sheet method: tiling x position finder (ImageJ macro)

> Not available (404 error)

### Compile NIfTI file from TIF(TIFF) stacks: .ipynb file

[Download Where?]()

> :warning: **Note:** This code has been tested only on Ubuntu. While it may work on other operating systems, compatibility and functionality are not guaranteed.

Preparations:

-   Install [ImageMagick](https://imagemagick.org/index.php)

-   Install [C3D](https://pypi.org/project/c3d/)

How to use: Please follow the instructions in the code.

### Stitching with Bigstitcher

Under review...

### 0-180 digree fusion by 3D slicer and Bigstitcher

Under review...

### descSpim parts list

(Change table display see Tables (how to display in R/Q Notes))

```{r}
#| include: false

# install.packages("kableExtra")
# install.packages("AER")
# install.packages("tinytex")
library(kableExtra)
library(magrittr)
library(shiny)
library(knitr)
library(tinytex)
library(AER)
library(tidyverse)
help("kableExtra")
help("kable")
```

```{r}
#| echo: false

descSPIM_part_list_230502 <- read.csv("/Users/marcelorosales/Documents/GitHub/Quarto/descSPIM_LSmicro/descSPIM_part_list_230502.csv")

kbl(descSPIM_part_list_230502, caption = "descSPIM parts list table") %>%
  kable_styling(bootstrap_options = "striped",
                full_width = F) 


```

```{r}
#| include: false
#| eval: false


descSPIM_part_list_230502 <- read.csv("/Users/marcelorosales/Documents/GitHub/Quarto/descSPIM_LSmicro/descSPIM_part_list_230502.csv")

descSPIM_part_list_230502
str(descSPIM_part_list_230502)

knitr::kable(descSPIM_part_list_230502, "pipe", align = "c")

```
